---
title: "Shaping the Transnational Public Sphere in the English press (revisions)"
author: "Cécile Armand"
date: "`r lubridate::today()`"
tags: [bilingual, press, structural topic modeling, transnational]  
abstract: |
  This document supplements the previous documentation destined to accompany the paper titled "Shaping the Transnational Public Sphere in Republican China: Discourses and Practices of the Rotary Club in the Shanghai press (1919-1949)" submitted to the *Journal of Digital History*. This second document provides the code for time-based topic modeling and named entity extraction (part 2), mapping locations (part 3), and semantic analysis (part 4) in the ProQuest collection of English-language periodicals. A similar document is devoted specifically to the Chinese-language newspaper *Shenbao*.  
  
   <style>
    body {
    text-align: justify}
  </style>
    
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    number_sections: false
    code_folding: show # hide
    fig_caption: true
    df_print: paged
---

```{r setup, include=FALSE, eval = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(histtext)
library(quanteda)
library(tidytext)
library(widyr)
library(sf)

```

# Populating the public sphere (Part 2)

## Filtering topics (Step 1)

Select the documents that contain at least 0.11% of topic 3 in the 5-topic model (1256 documents). 

```{r eval = FALSE}
library(tidyverse)
doc3 <- topicprop5 %>% filter(Topic3 > 0.11)  # 1256
```

## Refining text units (Step 2) 

Focus on "feature" articles and remove non-relevant genres of articles (984 documents remain)
```{r eval = FALSE}
doc3_filtered <- doc3 %>% filter(!category %in% c("Image/Photograph", "Obituary", "Stock Quote")) %>% filter(!DocId == "1420033734") 

doc_to_remove <- doc3_filtered %>%
  filter(
    str_detect(Title, "No Title|Brevities|BREVITIES|Men and Events|Notes|NOTES")
  ) %>% 
  filter(!category == ("Editorial, Commentary")) %>% 
  filter(!category == ("Letter to the Editor, Correspondence")) %>% 
  filter(!DocId == "1371424827") # 257 brevities to remove 

doc3_filtered <- doc3_filtered %>% filter(!DocId %in% doc_to_remove$DocId)

doc3_cat <- doc3_filtered %>% select(DocId, category) # select relevant metadata 

```
<br>
Retrieve the full text of documents using [histtext](https://bookdown.enpchina.eu/HistText_Book/query-functions.html#full-text-retrieval) (the current dataset contains only document ids), compute the length of articles (number of tokens) with [quanteda](https://quanteda.io/), and join with metadata (category): 
```{r eval = FALSE}

library(histtext)
library(quanteda)

doc3_ft <- get_documents(doc3_filtered, "proquest")
doc3_ft <- doc3_ft %>% mutate(length = ntoken(Text))
doc3_ft <- left_join(doc3_cat, doc3_ft) 
```

<br>
Export the dataset to check manually abnormally long articles 
```{r eval = FALSE}
write.csv(doc3_ft, "doc3_ft.csv")
```
<br>
Reimport shortened articles, remove these articles from the main list, and compile the two datasets to reconstitute the complete corpus with properly segmented news items:
```{r eval = FALSE}
library(readr)
doc3_short <- read_delim("doc3_short.csv", 
                         delim = ";", escape_double = FALSE, trim_ws = TRUE)

# remove these articles from the main list 

doc3_filtered <- doc3_ft %>% filter(!DocId %in% doc3_short$DocId)

# compile the two datasets using bind rows

doc3_filtered$Topic3 <- NULL
doc3_short <- doc3_short %>% mutate(DocId = as.character(DocId)) %>% mutate(Date = as.character(Date))

revised_eng <- bind_rows(doc3_filtered, doc3_short)  
```
<br>
The revised English corpus contains a total of 954 articles. 

Next, we create a customized list of stopwords to remove to improve the results of topic modeling. 

First, we retrieve the tokens and we compute their length: 
```{r eval = FALSE}
library(tidytext)

token <- revised_eng %>% select(DocId, Text)

token <- token %>% 
  unnest_tokens(output = token, input = Text) 

token_count <- token %>% group_by(token) %>% count() %>% mutate(length = nchar(token))

```
<br> 
Next, we create a preliminary list of stopwords by filtering tokens which appeared at least twice and contains at least 5 characters, and by removing non alphabetical characters (digits). 
```{r eval = FALSE}
stopwords <- token_count %>% filter(length>4) %>% filter(n >1) %>% 
  filter(!grepl("[[:digit:]]", token)) # remove digits
```
<br>
We export the raw list for manual refinement in Excel, we re-import the manually refined list and we transform it into a vector which can be used later for building topic models:
```{r eval = FALSE}
stopwords <- read_csv("stopwords.csv")
stopvec <- as.vector(stopwords)
stopvec<-unlist(stopvec)
stopvec<-unlist(stopvec)
```

## Time-based topic modelling (Step 3)

Define time windows
```{r eval = FALSE}

revised_eng %>% group_by(period) %>% count()

p1 <- revised_eng %>% filter(period == "1919-1929") # 184 articles
p2 <- revised_eng %>% filter(period == "1930-1937") # 687
p3 <- revised_eng %>% filter(period == "1938-1949") # 83 articles

```
<br>

<div class="alert alert-success" role="alert"> 
In the following, we focus on period 1. The same method was applied to the two later periods. To avoid repetition, we do not replicate the code. </div>

Build a 5-topic model using [stm](https://www.structuraltopicmodel.com/):  
```{r eval = FALSE}

# select metadata

meta <- p1 %>%  transmute(DocId, Title, Source, category, Date, Year, length)
meta <- as.data.frame(meta)

# create stm corpus object 

corpus <- stm::textProcessor(p1$Text,
                             metadata = meta, 
                             stem = FALSE, 
                             wordLengths = c(5, Inf), 
                             verbose = FALSE, 
                             customstopwords = stopvec)

stm::plotRemoved(corpus$documents, lower.thresh = c(0,10, by=5))

# chose 5 as the threshold for minimum frequency 

out <- stm::prepDocuments(corpus$documents, 
                          corpus$vocab, 
                          corpus$meta, 
                          lower.thresh = 5)
# 10562 of 11702 terms (17079 of 30220 tokens) are removed due to frequency. 
# The corpus now has 184 documents, 1140 terms and 13141 tokens.

# build the 5-topic model 

mod.5 <- stm::stm(out$documents, 
                  out$vocab, K=5, 
                  data=out$meta, 
                  prevalence =~ Year + Source + category, 
                  verbose = FALSE)


```
<br>
Estimate the effects of time (year) and source (periodical) on topic prevalence: 
```{r eval = FALSE}
year5 <- stm::estimateEffect(1:5 ~ Year, mod.5, meta=out$meta)
source5 <- stm::estimateEffect(1:5 ~ Source, mod.5, meta=out$meta)
```
<br>
Explore the topics
```{r eval = FALSE}
plot.STM(mod.5,"summary", n=5)
```
<br>

## Topical clusters

This section explains how to cluster documents based on their topic proportions using Principal Component Analysis (PCA) and Hierarchical Clustering (HCPC).

Extract topic proportions: 
```{r eval = FALSE}
topicprop5<-make.dt(mod.5, meta)
```
<br>
Prepare the data for PCA: 
```{r eval = FALSE}
pca5 <- topicprop5 %>% select(DocId, Topic1, Topic2, Topic3, Topic4, Topic5)
pca5 <- pca5 %>% column_to_rownames("DocId")
```
<br>
Load the [FactoMineR](http://factominer.free.fr/) package and run PCA and HCPC functions: 
```{r eval = FALSE}
library(FactoMineR)

res.PCA<-PCA(pca5,graph=FALSE)
res.HCPC<-HCPC(res.PCA,nb.clust=5,consol=FALSE,graph=FALSE)
```

<br> 
Optionally, plot the results of PCA and HCPC: 
```{r eval = FALSE}
plot.PCA(res.PCA,choix='var',title="PCA graph of variables (topic proportions)")
plot.PCA(res.PCA,title="PCA graph of individuals (documents)")
```
<br> 
Extract and relabel topical clusters
```{r eval = FALSE}
pca_clusters <- as.data.frame(res.HCPC$data.clust)
pca_clusters <- rownames_to_column(pca_clusters, "DocId") %>% select(DocId, clust) %>% rename(clust5 = clust)
pca_clusters <- pca_clusters %>% mutate (label5 = fct_recode(clust5, "American education" = "1", 
                                                             "Pacific relations" = "2", 
                                                             "Water conservancy and public health" = "3", 
                                                             "Labor, industry, and Soviet Russia" = "4", 
                                                             "International peace" = "5"))
```
<br> 
Join clusters with other metadata: 
```{r eval = FALSE}
pca_clusters_meta <- left_join(pca_clusters, meta)
```

## Retrieving actors (Step 4)

<div class="alert alert-success" role="alert"> 
In the following, we focus on period 1. The same method was applied to the two later periods. To avoid repetition, we do not replicate the code. </div>

Extract named entities using histtext [ner_on_df](https://bookdown.enpchina.eu/HistText_Book/named-entity-recognition-ner.html#ner-on-external-documents) function: 
```{r eval=FALSE }

library(histtext)
ner_eng <- ner_on_df(p1, "Text", id_column="DocId", model = "spacy:en:ner")

```
<br>
Select entities of interest (persons, organizations, locations): 
```{r eval = FALSE}

pers_eng <- ner_eng %>% filter(Type == "PERSON")
org_eng <- ner_eng %>% filter(Type == "ORG")
loc_eng <- ner_eng %>% filter(Type %in% c("LOC", "GPE"))

```

### Persons 

Data cleaning on persons names. 

First, remove special characters and digits and convert names to title case: 
```{r eval = FALSE}

p1_pers_eng <- p1_pers_eng %>% mutate(Text_clean = str_remove_all(Text, "[:digit:]")) %>%
  mutate(Text_clean = str_replace(Text_clean,"- ","")) %>%
  mutate(Text_clean = str_replace(Text_clean," -","")) %>%
  mutate(Text_clean = str_squish(Text_clean))  %>%
  mutate(Text_clean = str_remove_all(Text_clean, "'s"))%>% 
  mutate(Text_clean2 = str_replace(Text_clean, "^\\.", "")) %>% 
  mutate(Text_clean2 = str_replace(Text_clean2, "^\\--", ""))%>% 
  mutate(Text_clean2 = str_replace(Text_clean2, "^\\-", ""))%>% 
  mutate(Text_clean2 = str_replace(Text_clean2, "^\\'", ""))%>%
  mutate(Text_clean2 = str_squish(Text_clean2)) %>% 
  mutate(Text_clean2 = str_replace(Text_clean2, "\\''$", ""))%>% 
  mutate(Text_clean2 = str_replace(Text_clean2, "\\'$", ""))%>% 
  mutate(Text_clean2 = str_replace(Text_clean2, "\\--$", "")) %>% 
  mutate(Text_clean2 = str_replace(Text_clean2, "\\-$", ""))%>%
  mutate(Text_clean2 = str_replace(Text_clean2, " 'R", " R"))%>% 
  mutate(Text_clean2 = str_remove_all(Text_clean2, "''")) %>% 
  mutate(Text_clean2 = str_replace_all(Text_clean2, " '", " ")) %>% 
  mutate(Text_clean2 = str_replace_all(Text_clean2, "' ", " "))%>% 
  mutate(Text_clean2 = str_replace_all(Text_clean2, " . ", " "))%>%
  mutate(Text_clean2 = str_to_title(Text_clean2)) 

```
<br>
Remove titles (Dr, Mr)
```{r eval = FALSE}

p1_pers_eng <- p1_pers_eng %>% 
  mutate(Text_clean2 = str_replace(Text_clean2, "Dr ", ""))%>% 
  filter(!Text_clean2 %in% c("Mr", "Dr"))

```
<br>
Replace empty strings with NA and remove NA values: 
```{r eval = FALSE}
# replace empty strings by NA

p1_pers_eng$Text_clean2[p1_pers_eng$Text_clean2==""] <- NA

# remove NAs

p1_pers_eng <- p1_pers_eng %>% drop_na(Text_clean2)

```
<br>
Compute basic statistics to assist further data cleaning:  
```{r eval = FALSE}

# measure text length to identify anomalies and eliminate persons names that contain less than 2 characters

p1_pers_eng <- p1_pers_eng %>%  
  mutate(length = nchar(Text_clean2)) %>%
  filter(length >1)

# count names frequency 

p1_pers_eng <- p1_pers_eng %>%
  group_by(Text_clean2) %>% add_tally()

# count number of tokens to identify compound names or incomplete names   

p1_pers_eng <- p1_pers_eng %>% mutate(token = ntoken(Text_clean2))

```
<br>
Export dataset to finish manually  
```{r eval = FALSE}
write.csv(p1_pers_eng, "p1_pers_eng.csv")
```

### Organizations 

Data cleaning of organizations. 

First, remove OCR noise and standardize names variants: 
```{r eval = FALSE}

p1_org_eng <- p1_org_eng %>% 
  mutate(Text_clean = str_replace(Text, "'s$", "")) %>% 
  mutate(Text_clean = str_replace(Text_clean, " s$", "")) %>% 
  mutate(Text_clean = str_to_title(Text_clean)) %>% 
  mutate(Text_clean = str_replace(Text_clean, "Mctyeire", "McTyeire")) %>% 
  mutate(Text_clean = str_replace(Text_clean, "^The ", "")) %>% 
  mutate(Text_clean = str_replace(Text_clean, "^He ", ""))%>% 
  mutate(Text_clean = str_squish(Text_clean)) %>% 
  mutate(Text_clean = str_replace(Text_clean, "^-", "")) %>% 
  mutate(Text_clean = str_replace(Text_clean, "-$", "")) %>% 
  mutate(Text_clean = str_replace(Text_clean, "^''", "")) %>% 
  mutate(Text_clean = str_replace(Text_clean, "^'", "")) %>% 
  mutate(Text_clean = str_replace(Text_clean, "'$", "")) %>% 
  mutate(Text_clean = str_replace(Text_clean, ". ''$", "")) %>% 
  mutate(Text_clean = str_replace(Text_clean, ". '$", "")) %>% 
  mutate(Text_clean = str_squish(Text_clean)) %>% 
  mutate(Text_clean = str_replace(Text_clean, "1 Curtis", "Curtis")) %>% 
  mutate(Text_clean = str_replace(Text_clean, "Co$", "Company"))  %>% 
  mutate(Text_clean = str_replace(Text_clean, "Co Ltd$", "Company")) %>% 
  mutate(Text_clean = str_replace(Text_clean, "Co Inc$", "Company")) %>% 
  mutate(Text_clean = str_replace(Text_clean, "Com Pany", "Company"))  %>% 
  mutate(Text_clean = str_replace(Text_clean, "Corpora$", "Corporation"))%>% 
  mutate(Text_clean = str_replace(Text_clean, "Corp$", "Corporation"))%>% 
  mutate(Text_clean = str_replace(Text_clean, "Mfg 5 Mrg", "Manufacturing")) %>% 
  mutate(Text_clean = str_replace(Text_clean, "Mfg", "Manufacturing"))  
```
<br>
Count length and export for manual refinement: 
```{r eval = FALSE}

p1_org_eng <- p1_org_eng %>% mutate(length = nchar(Text_clean)) 
write.csv(p1_org_eng, "p1_org_eng.csv")

```
<br>
Reload cleaned data
```{r eval = FALSE}

library(readr)
p1_org_eng_clean <- read_delim("p1_org_eng_clean.csv", 
                               delim = ";", escape_double = FALSE, trim_ws = TRUE)

write.csv(p1_org_eng_clean, "p1_org_eng_clean.csv")
```
<br>
Count frequencies
```{r eval = FALSE}
p1_org_eng_clean_count <- p1_org_eng_clean %>% distinct(DocId, Text_clean) %>% group_by(Text_clean) %>% count()
```
<br>
Extract the class of organizations: 
```{r eval = FALSE}

# create vectors of classifiers

class <- as.vector(c("Association", "Club", "College", "School", "University", 
                     "Company", "Corporation", 
                     "Army", "Corps", "Navy", 
                     "Hospital", "Clinic", 
                     "Government", "Council", "Commission", "Administration",
                     "Congress", "Parliament", "House",
                     "Press", "News", "Times", "Tribune","Journal", "Magazine", "Pao", "Herald"))
classvec<-unlist(class)
classvec2 <- paste(classvec, sep = "", collapse = "|")

# extract the terms listed 

p1_org_eng_clean <- p1_org_eng_clean %>% mutate(class2 = str_extract(Text_clean, classvec2)) 

# count number of organizations in each category

class_count <- p1_org_eng_clean %>% distinct(Text_clean, class2) %>% group_by(class2) %>% count(sort = TRUE)
```

# Mapping the Public Sphere (Part 3)

## Countries
```{r eval = FALSE}

# load locations data 

loc_map <- read_delim("maps/loc_map.csv", 
                      delim = ";", escape_double = FALSE, trim_ws = TRUE)

# select countries 

loc_map_country  <-  loc_map %>% mutate(Country = Place) %>% mutate(Prov_Py = Province) %>% 
  filter(Type == "Country") %>% mutate(Prov_Py = Province) %>% 
  select(Language, Period, Type, Country, Count)

# load packages

install.packages("tmap", repos = c("https://r-tmap.r-universe.dev",
                                   "https://cloud.r-project.org"))
library(tmap)    # for static and interactive maps
library(leaflet) # for interactive maps
library(sf)
library(maps)

# load country data

world_name <- world %>% as.data.frame()
world_name <- world_name %>% rename(Country = name_long)

# join with my list of countries

loc_map_country <- inner_join(loc_map_country, world_name)
loc_map_country_eng <- loc_map_country %>% filter(Language == "English")

# compute mean frequencies across period

loc_map_country_eng_mean <- loc_map_country_eng %>% 
  group_by(Country, iso_a2, geom) %>% 
  summarise(mean = round(mean(Count), 0)) %>% ungroup()

# convert dataframe into shapefile 

loc_map_country_eng_sf <- st_as_sf(loc_map_country_eng_mean, sf_column_name = "geom", crs = "WGS84")

# Create a color palette for the map:

mypalette_eng <- colorBin( palette="Blues", domain=loc_map_country_eng_mean$mean, na.color="transparent", bins = 5)

# create choropleth map

leaflet(loc_map_country_eng_sf) %>% 
  addTiles()  %>% 
  setView( lat=10, lng=0 , zoom=2) %>%
  addPolygons( stroke = FALSE, fillOpacity = 0.9, smoothFactor = 0.5, color = ~colorBin("Blues", mean)(mean) ) %>%
  addLegend( pal=mypalette_eng, values=~mean, opacity=0.9, title = "Mean frequency", position = "bottomleft" )


```

## Cities

```{r eval = FALSE}

# create city data

loc_map_zh_to_join <-  loc_map %>% mutate(Name = Place) %>% mutate(Prov_Py = Province) %>% filter(Country == "China")

# Chinese cities/provinces

MCGD_Data2023.06.21 <- read.csv("~/publicsphere/maps/MCGD_Data2023-06-21.csv")
mcgd <- MCGD_Data2023.06.21

# join with Chinese coordinates 

zh_city <- inner_join(loc_map_zh_to_join, mcgd)

missing <- setdiff(loc_map_zh_to_join$Name, zh_city$Name)
missing <- as.data.frame(missing)

write.csv(zh_city, "zh_city.csv")

# reload clean data

zh_city2 <- read_delim("maps/zh_city2.csv", 
                       delim = ";", escape_double = FALSE, trim_ws = TRUE)

# filter non Chinese cities

loc_map_cities <-  loc_map %>% mutate(Name = Place) %>% filter(Type == "City") %>% filter(!Country == "China")

# join with geocoordinates

library(maps)
data(world.cities)

world_cities <- world.cities %>% as.data.frame()
world_cities2 <- world_cities %>% mutate(name = str_remove_all(name, "'"))
world_cities2 <- world_cities2 %>% select(Name, country.etc, lat, long)

loc_map_cities_latlong <- inner_join(loc_map_cities, world_cities2)
loc_map_cities_latlong <- left_join(loc_map_cities, world_cities2)

# find duplicates 

pb <- loc_map_cities_latlong %>% group_by(Name, country.etc) %>% count() %>% filter(n>1)

# reload cleaned cities 

cities_clean <- read_delim("cities_clean.csv", 
                           delim = ";", escape_double = FALSE, trim_ws = TRUE)

cities_to_join <- cities_clean %>% select(Language, Period, Country, Name, Count, lat, long)

zh_city2_to_join <- zh_city2 %>% select(Language, Period, Country, Name, Count, LAT, LONG) %>% rename(lat = LAT, long = LONG)  

all_cities <- bind_rows(cities_to_join, zh_city2_to_join)

all_cities <- all_cities %>% mutate(City = str_replace(Name, "Jiangsu", "Shanghai"))

# filter by language 

all_cities_eng <- all_cities %>% filter(Language == "English")

# compute mean 

loc_map_city_eng_mean <- all_cities_eng %>% 
  group_by(Name, lat, long) %>% 
  summarise(mean = round(mean(Count), 0)) %>% ungroup()

# map with leaflet

loc_map_city_eng_mean %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers( radius = ~log(mean)*2.5,
                    label = ~Name,
                    color = "white",
                    weight = 2,
                    opacity = 0.6,
                    fill = TRUE,
                    fillColor = "blue",
                    fillOpacity = 0.9,
                    stroke = TRUE,
                    popup = ~paste( "City:", Name ,
                                    "",
                                    "Mean frequency:", mean))


```


# Articulating the Public Sphere (Part 4)

## Bigrams

Create bigrams
```{r eval = FALSE}

# load packages

library(tidyverse)
library(tidytext)

eng_bigram <- doc3_ft %>% 
  unnest_tokens(output = bigram, 
                input = Text, 
                token = "ngrams", 
                n = 2)

# preliminary cleaning 

eng_bigram <- eng_bigram %>% mutate(bigram = str_remove_all(bigram, "[:digit:]"))  %>% 
  mutate(bigram = str_replace_all(bigram, "[[:punct:]]", ""))%>% 
  filter(!str_detect(bigram, '[0-9]{1,}')) %>% 
  mutate(bigram = str_remove_all(bigram, "'s")) %>%
  mutate(bigram = str_remove_all(bigram, "'")) %>%
  mutate(bigram = str_remove_all(bigram, "'")) %>% ) 
  mutate(bigram = str_squish(bigram)) %>% 
  mutate(bigram = str_replace_all(bigram, "na tions", "nations"))%>% 
  mutate(bigram = str_replace_all(bigram, "na tion", "nation")) %>% 
  mutate(bigram = str_replace_all(bigram, "na tional", "national"))%>% 
  mutate(bigram = str_replace_all(bigram, "inter national", "international"))%>% 
  mutate(bigram = str_replace_all(bigram, "inter nationally", "internationally"))%>% 
  mutate(bigram = str_replace(bigram, "^ternational", "international"))

# separate bigrams into words for further cleaning
  
eng_bigram_separated <- eng_bigram %>%
  separate(bigram, c("word1", "word2"), sep = " ")

# remove stop words and other non words

eng_bigram_filtered <- eng_bigram_separated %>% 
  rename(word = word1) %>%
  anti_join(stop_words) %>% 
  filter(!str_detect(word, '[0-9]{1,}')) %>% 
  filter(nchar(word) > 3) %>% 
  filter(!word %in% c("tion", "tions", "chin", "ment")) %>%
  mutate(word = str_remove_all(word, "'s")) %>%
  mutate(word = str_remove_all(word, "'")) %>%
  rename(word1 = word) %>% 
  rename(word = word2) %>%
  anti_join(stop_words) %>% 
  filter(!str_detect(word, '[0-9]{1,}')) %>% 
  filter(nchar(word) > 3) %>% 
  filter(!word %in% c("tion", "tions", "chin", "ment")) %>%
  rename(word2 = word)   

# reunite bigrams

eng_bigram_united <- eng_bigram_filtered %>%
  unite(bigram, word1, word2, sep = " ")

# count bigrams 

eng_bigram_count <- eng_bigram_united %>%
  count(bigram, sort = TRUE)

# Join with metadata to identify the most frequent bigrams by period

eng_bigram_united_meta <- left_join(eng_bigram_united, meta)

```

### Transnational

Focus on bigrams centered on "international" and filter irrelevant terms: 
```{r eval = FALSE}

internat_bigram <- eng_bigram_filtered %>% filter(word1 == "international") %>% 
  filter(!word2 == "international") %>% 
  filter(!word2 %in% c("addressed", "arrived", "approximately"))

```

<br>
Count frequencies and tf-idf by period 
```{r eval = FALSE}
# count bigrams 

internat_bigram_count <- internat_bigram %>%
  count(bigram, sort = TRUE)

# tf idf by period
internat_bigram_tf_idf_period <- internat_bigram_united_clean %>%
  count(period, bigram_clean) %>%
  bind_tf_idf(bigram_clean, period, n) %>%
  arrange(desc(tf_idf))

# visualize 

internat_bigram_tf_idf_period %>%
  group_by(period) %>%
  top_n(10, tf_idf) %>%
  ungroup() %>%
  mutate(bigram_clean = reorder(bigram_clean, tf_idf)) %>%
  ggplot(aes(tf_idf, bigram_clean, fill = period)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ period, scales = "free", ncol=3) +
  labs(x = "tf-idf", y = "bigram", 
       title = "Highest tf-idf bigrams associated with \"international\" in the Rotary Club corpus", 
       subtitle = "tf-idf by period", 
       caption = "Based on ProQuest \"Chinese Newspapers Collection (CNC)\"")


```

### Public 

Focus on bigrams centered on "public"
```{r eval = FALSE}
public_bigram <- eng_bigram_filtered %>% filter(word1 == "public")
```
<br>
Count frequencies and tf-idf by period 
```{r eval = FALSE}
# count bigrams 

public_bigram_count <- public_bigram %>%
  count(bigram, sort = TRUE)

# tf idf by period
public_bigram_tf_idf_period <- public_bigram_united_clean %>%
  count(period, bigram_clean) %>%
  bind_tf_idf(bigram_clean, period, n) %>%
  arrange(desc(tf_idf))

# visualize 

public_bigram_tf_idf_period %>%
  group_by(period) %>%
  top_n(10, tf_idf) %>%
  ungroup() %>%
  mutate(bigram_clean = reorder(bigram_clean, tf_idf)) %>%
  ggplot(aes(tf_idf, bigram_clean, fill = period)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ period, scales = "free", ncol=3) +
  labs(x = "tf-idf", y = "bigram", 
       title = "Highest tf-idf bigrams associated with \"public\" in the Rotary Club corpus", 
       subtitle = "tf-idf by period", 
       caption = "Based on ProQuest \"Chinese Newspapers Collection (CNC)\"")

```

## Collocates 

Create collocates (including bigrams) using [quanteda](https://quanteda.io/) 
```{r eval = FALSE}

library(quanteda)
library(quanteda.textstats)

eng_tokens <- tokens(docs3_ft$Text) %>%
  tokens_remove(stopwords("english")) 
eng_colloc <- textstat_collocations(eng_tokens, size = 2, min_count = 2) 


eng_colloc_clean <- eng_colloc %>% 
  filter(!str_detect(collocation, '[0-9]{1,}')) %>% 
  mutate(collocation = str_remove_all(collocation, "'s")) %>%
  mutate(collocation = str_remove_all(collocation, "'")) %>%
  mutate(collocation = str_remove_all(collocation, "'")) 

eng_colloc_clean <- eng_colloc %>% mutate(collocation = str_remove_all(collocation, "[:digit:]"))  %>% 
  mutate(collocation = str_replace_all(collocation, "[[:punct:]]", "")) %>% 
  mutate(collocation = str_squish(collocation)) %>% 
  mutate(collocation = str_replace_all(collocation, "na tions", "nations"))%>% 
  mutate(collocation = str_replace_all(collocation, "na tion", "nation")) %>% 
  mutate(collocation = str_replace_all(collocation, "na tional", "national"))%>% 
  mutate(collocation = str_replace_all(collocation, "inter national", "international"))%>% 
  mutate(collocation = str_replace_all(collocation, "inter nationally", "internationally"))%>% 
  mutate(collocation = str_replace(collocation, "^ternational", "international"))

# replace empty strings by NA

eng_colloc_clean$collocation[eng_colloc_clean$collocation==""] <- NA

# remove NA 
eng_colloc_clean <- eng_colloc_clean %>% drop_na(collocation)

eng_colloc_clean <- eng_colloc_clean %>% mutate(length = nchar(collocation)) %>% mutate(ntoken = ntoken(collocation))

# remove tokens with less than 4 characters

eng_colloc_clean <- eng_colloc_clean %>% filter(length > 3) 

# merge tokens and collocations

corpus_tokens <- tokens_compound(eng_tokens, eng_colloc_clean)

minimumFrequency <- 2

# Create DTM, prune vocabulary and set binary values for presence/absence of types
binDTM <- corpus_tokens %>% 
  tokens_remove("") %>%
  dfm() %>% 
  dfm_trim(min_docfreq = minimumFrequency, max_docfreq = 1000000) %>% 
  dfm_weight("boolean")

```

<br> 
Convert document-term matrix into tidydaframe to compute pairwise count, clean the data and remove stopwords: 
```{r eval = FALSE}

# convert DTM into tidy dataframe 

library(dplyr)
library(tidytext)

eng_td <- tidy(binDTM)

# count pairwise 

library(widyr)

word_pairs <- eng_td %>%
  pairwise_count(term, document, sort = TRUE)

# remove non words based on their length

word_pairs <- word_pairs %>% mutate(l1 = nchar(item1)) %>% mutate(l2 = nchar(item2))
word_pairs_filtered <- word_pairs %>% filter(l1>3) %>% filter(l2>3)

# create list of stopwords to remove 

stop_words <- c("one", "even", "now", "much", "can", "made", "still", "may", "well", "yet", "make", "first", "since", 
                "re", "also", "said","ing", "take", "two", "every", "whole", "among","tion", "just", "however", "ed", 
                "last","taken","lo", "enough", "come", "upon", "another", "without", "found", "s", "done", "put", "told", 
                "given","might","met", "brought", "although","gave", "less", "perhaps", "th","ol","pro", "led", "find", "de", 
                "us", "ex", "ion", "tho", "nil", "certainly", "held", "arc", "toward", "rather", "bring", "china's", "con", "seen", 
                "see", "indeed", "get", "shown", "go", "later", "stated", "really", "often", "oi", "ihe","taking", "felt", "hi", "ho", 
                "strongly", "always", "used", "per", "im", "lias", "showed", "look", "spoke", "says", "three", "already", "able", "therefore", 
                "etc", "comes", "though", "especially", "ii", "due", "en", "al", "cf", "pointed","lor", "extremely", "left", "says", "tlie", "let", 
                "shall", "thus", "ly", "whose", "ot", "ha", "se", "dis", "ten", "latter", "third", "hold", "con_ditions", "spite", "govern_ment", 
                "owing", "hie", "ad", "un", "must", "within","went", "many", "ment", "give")

stop_words <- as.data.frame(stop_words)

# remove stop words 

word_pairs_filtered <- word_pairs_filtered %>% filter(!item1 %in% stop_words$stop_words) %>% 
  filter(!item2 %in% stop_words$stop_words)

```

### Transnational

Select collocates of "international" and "national"
```{r eval = FALSE}

nation_inter <- word_pairs_filtered %>% filter(item1 %in% c("national", "international"))
nation_inter <- nation_inter %>% select(item1, item2, n) %>% rename(cooc = n)

```
<br>
Create a node list of words with their frequencies
```{r eval = FALSE}

nation_inter_node <- nation_inter %>% select(item2) %>% unique() %>% rename(word = item2)
word_count <- eng_tidy_token_filtered %>% group_by(word) %>% add_tally() %>% select(word, n) %>% unique()
word_count <- word_count %>% rename(count = n)
nation_inter_node <- inner_join(nation_inter_node, word_count)

```
<br> 
Compute word frequencies and join frequencies with the list of words
```{r eval = FALSE}

eng_tidy_token_filtered %>% group_by(word) %>% add_tally() 
word_count <- eng_tidy_token_filtered %>% select(word, n) %>% unique()
word_count <- word_count %>% rename(count = n)
nation_inter_node <- inner_join(nation_inter_node, word_count)

```
<br>
Filter pairs with weight > 100 
```{r eval = FALSE}
nation_inter_filtered <- nation_inter %>% filter(cooc > 100)
```
<br>
Build a co-ocurrence network with [igraph](https://r.igraph.org/)
```{r eval = FALSE}

library(igraph)

e.list <- nation_inter_filtered
v.attr <- nation_inter_node_filtered

G <- graph.data.frame(e.list, vertices=v.attr, directed=FALSE)

v.size <- V(G)$count # index node size to words frequencies
v.label <- V(G)$name
E(G)$weight <- E(G)$cooc # index edge weight to pairs frequencies
eigenCent <- evcent(G)$vector # index node color to their eigenvector centrality 

head(eigenCent, 20)

plot(sort(eigenCent, decreasing=TRUE), type="l")

bins <- unique(quantile(eigenCent, seq(0,1,length.out=30)))
vals <- cut(eigenCent, bins, labels=FALSE, include.lowest=TRUE)

colorVals <- rev(heat.colors(length(bins)))[vals]
V(G)$color <- colorVals

l <- layout.fruchterman.reingold(G)


plot(G, 
     layout=l,
     edge.width=E(G)$weight*0.01,
     vertex.size=v.size*0.01, 
     vertex.label=v.label,
     vertex.label.cex=v.size*0.001,
     vertex.label.color="black", 
     vertex.label.dist=0.2,
     vertex.label.family="Arial")

```
<br>
Refine network visualization with [tidygraph](https://tidygraph.data-imaginist.com/) and [gggraph](https://github.com/thomasp85/ggraph)
```{r eval = FALSE}

library(tidygraph)
library(ggraph)

tg <- tidygraph::as_tbl_graph(G) %>% activate(nodes) %>% mutate(label=name)

v.size <- V(tg)$count
E(tg)$weight <- E(tg)$cooc
eigenCent <- evcent(tg)$vector
bins <- unique(quantile(eigenCent, seq(0,1,length.out=30)))
vals <- cut(eigenCent, bins, labels=FALSE, include.lowest=TRUE)
colorVals <- rev(heat.colors(length(bins)))[vals]


tg %>%
  ggraph(layout="stress") +
  geom_edge_link(alpha = .25, colour='white', aes(width = weight)) +
  geom_node_point(size=log(v.size)*2, color=colorVals) +
  geom_node_text(aes(label = name), repel = TRUE, point.padding = unit(0.2, "lines"), size=log(v.size), colour="white") +
  theme_graph(background = 'grey20')

```

<br>
Create biplot of collocates 
```{r eval = FALSE}

# select term of interest (international)

international <- "international" 

# calculate co-occurrence statistics using log-likelihood (LOGLIK)

source("https://tm4ss.github.io/calculateCoocStatistics.R") # load function for co-occurrence calculation

coocs <- calculateCoocStatistics(international, DTM, measure="LOGLIK")

# reduce document-term matrix 

redux_dfm <- dfm_select(DTM, 
                        pattern = c(names(coocs)[1:100], "international"))

tag_fcm <- fcm(redux_dfm)

coocdf <- coocs %>%
  as.data.frame() %>%
  dplyr::mutate(CollStrength = coocs,
                Term = names(coocs)) 

coocdf_filtered <- coocdf %>%
  dplyr::filter(CollStrength > 13) 


# create matrix of collocates

library(Matrix)

collocates <- t(binDTM) %*% binDTM
collocates <- as.matrix(collocates)

coolocs <- c(coocdf_filtered$Term, "international")

# remove non-collocating terms
collocates_redux <- collocates[rownames(collocates) %in% coolocs, ]
collocates_redux <- collocates_redux[, colnames(collocates_redux) %in% coolocs]

# create biplot of collocates 

library(FactoMineR)
library(factoextra)

res.ca <- CA(collocates_redux, graph = FALSE)

fviz_ca_row(res.ca, repel = TRUE, col.row = "gray20", title = "Collocates of *international* in the Rotary corpus")
```

### Public 

Select collocates of "public" based bigrams
```{r eval = FALSE}

# create list of bigrams 

list <- c("public_opinion", "public_spirited", "public_spirit",
          "public_service", "public_services", "public_affairs", 
          "public_welfare", "public_utility", "public_utilities")
list <- as.data.frame(list)
list <- list %>% rename(item1 = list)

# select bigrams in list of collocates 

public_cooc <- word_pairs_filtered %>% filter(item1 %in% list$item1)

# filter pairs with a weight > 5 

public_cooc <- public_cooc %>% rename(cooc = n) 
public_filtered <- public_cooc %>% filter(cooc > 5)

```
<br>
Create node list of words 
```{r eval = FALSE}
public_node_filtered1 <- public_filtered %>% select(item1) %>% unique() %>% rename(word = item1)
public_node_filtered2 <- public_filtered %>% select(item2) %>% unique() %>% rename(word = item2)
public_node_filtered <- bind_rows(public_node_filtered1, public_node_filtered2)
public_node_filtered <- public_node_filtered %>% unique()
public_node_filtered <- inner_join(public_node_filtered, word_count)
```
<br>
Build a co-ocurrence network with [igraph](https://r.igraph.org/)
```{r eval = FALSE}
library(igraph)

e.list <- public_filtered
v.attr <- public_node_filtered

G <- graph.data.frame(e.list, vertices=v.attr, directed=FALSE)

v.size <- V(G)$count
v.label <- V(G)$name
E(G)$weight <- E(G)$cooc
eigenCent <- evcent(G)$vector

head(eigenCent, 20)

plot(sort(eigenCent, decreasing=TRUE), type="l")

bins <- unique(quantile(eigenCent, seq(0,1,length.out=30)))
vals <- cut(eigenCent, bins, labels=FALSE, include.lowest=TRUE)

colorVals <- rev(heat.colors(length(bins)))[vals]
V(G)$color <- colorVals

l <- layout.fruchterman.reingold(G)


plot(G, 
     layout=l,
     edge.width=E(G)$weight*0.01,
     vertex.size=v.size*0.015, 
     vertex.label=v.label,
     vertex.label.cex=v.size*0.002,
     vertex.label.color="black", 
     vertex.label.dist=0.2,
     vertex.label.family="Arial")
```

<br>
Refine network visualization with [tidygraph](https://tidygraph.data-imaginist.com/) and [gggraph](https://github.com/thomasp85/ggraph)
```{r eval = FALSE}

tg <- tidygraph::as_tbl_graph(G) %>% activate(nodes) %>% mutate(label=name)

v.size <- V(tg)$count
E(tg)$weight <- E(tg)$cooc
eigenCent <- evcent(tg)$vector
bins <- unique(quantile(eigenCent, seq(0,1,length.out=30)))
vals <- cut(eigenCent, bins, labels=FALSE, include.lowest=TRUE)
colorVals <- rev(heat.colors(length(bins)))[vals]


tg %>%
  ggraph(layout="stress") +
  geom_edge_link(alpha = .25, colour='white', aes(width = weight)) +
  geom_node_point(size=log(v.size)*1.5, color=colorVals) +
  geom_node_text(aes(label = name), repel = TRUE, point.padding = unit(0.2, "lines"), size=log(v.size), colour="white") +
  theme_graph(background = 'grey20')

```


